combined

### 2021-10-20 analysis/combined.Rmd
as

```{r}
params %>%

  pivot_wider(id_cols = trt,
              names_from = "term", 
              values_from = "estimate") %>% 
  mutate(slope = - slope) -> distance_final
```

@@

```{r}
fig2 <- fig1 %>% 
  left_join(label)
```

>>>>

```{r}
params %>% 
  pivot_wider(id_cols = trt,
              names_from = "term", 
              values_from = "estimate") %>% 
  mutate(slope = - slope) -> distance_final
```

@@

```{r}
library(tidyverse)
fig2 <- fig1 %>% 
  left_join(label)
```
